---
title: "hypothesis testing"
author: "Joshua Gichana"
date: "2022-12-04"
output: html_document
---
We are going to test if there is a difference in closing prices between the Swiss SMI and French CAC .

**The null and alternative hypotheses are :**
 H0 :difference in means equals 0
        vs
 H1 : difference in means is not equal to 0
 
**The test and significance level **

- From the data we have two parameters hence we will use a two-sample test
and since we don't have the population variance ,the test will be a t-test.
- we will chose a significance level alpha = 0.05

**Loading the data...**

```{r}
data(EuStockMarkets)
```

**next we extract variables from the data**

```{r}
SMI <- EuStockMarkets[,2]
CAC <- EuStockMarkets[,3]
```

**we will now perform the hypothesis testing.**

```{r}
t.test(SMI , CAC , alternative = 'two.sided' , mu = 0 , conf.level = 0.95)
```

**Conclusion**

We find a p-value less than alpha = 0.05 so we can reject the null and conclude that there are differences in closing prices between the Swiss SMI and French CAC stock indices.
